Are kelp forests different? A comparison of kelp forests between contrasting

### 2018-07-25 paper_draft.Rmd
wave and temperature data uploaded

---
title: "Are kelp forests different? A comparison of kelp forests between contrasting study sites"
output:
  pdf_document:
    toc: yes
  html_notebook:
    css: C:/Program Files/R/r_working_directory/benthic_paper/ecography.csl
    fig_caption: yes
    fig_height: 5
    fig_width: 4
    toc: yes
  word_document:
    toc: yes
bibliography: mycollection.bib
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(include = TRUE, echo = FALSE, warning = FALSE,
                      message = FALSE, tidy = FALSE, cache = FALSE,
                      fig.align = 'center',
                      fig.show = 'hold', fig.path = 'figures/')
```

@@

The sea urchin _P. angulosus_ is the dominant herbivore in South African kelp forests along the south-west coast [@Velimirov1977; @Field1980; @Leliaert2000] however, turbulent waters and its small size prevent it from feeding on adult kelps. I Instead the urchin is restricted to feeding mostly on kelp detritus, but also on juvenile kelps [@Fricke1979; @Day2002]. The abalone Haliotis midae is also a notable herbivore in this ecosystem, but it too feeds predominantly on kelp detritus [@Tarr1996; @Mayfield2000]. This abalone is closely associated with _P. angulosus_, whereby juvenile abalone take refuge beneath urchin spines [@Day2000a; @Day2000b; @Mayfield2000].The west coast rock lobster _J. lalandii_ is known for its role in maintaining alternative stable states [@Barkai1988] and is a major predator of both _P. angulosus_ and juvenile H. midae @Mayfield2001; @BlameyBranch2012], particularly east of Cape Point where subtidal mussel beds are scarce. In the early 1990s, _J. lalandii_ expanded its distribution east of False Bay [@Cockcroft2008]. Following the ‘invasion’ of rock lobsters, herbivore numbers declined significantly, most likely as a result of direct lobster predation, which resulted in an increased abundance of macroalgae and sessile invertebrates [@Blamey2010; @Blamey2012]. This suggests that the invasion of _J. lalandii_ into these areas has resulted in the establishment of an alternative stable-state [@Blamey2012] and is an excellent example of the role that predators can play in transforming the structure and functioning of ecosystems, without directly disturbing kelp themselves.

@@

All data analyses were done using the R software (R Core Team, 2016), and the vegan package (Oksanen et al. 2016) and ggplot2 (Wickham 2009). The Shapiro-Wilk normality test was run before any analyses to investigate the distribution of the data. All benthic data were first 4th root transformed before any analyses were run to down-weigh species that had high biomass values and low abundance values, as this may have affected the ordination analysis. The transformed data was then used to generate a Bray-Curtis similarity matrix.

@@

```{r diversity fauna script, message=FALSE, warning=FALSE, paged.print=FALSE}

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = TRUE ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'white', colour = 'white')) +
              ylab("") + 
              xlab("") +
              coord_flip()
```

```{r biomass barplot, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap='Comparison of raw biomass species data between sites. Graph A represents flora and graph B represents fauna.'}
ggarrange(plot_flora, plot_fauna, ncol = 2, nrow = 1, labels = "AUTO", legend = "bottom", common.legend = TRUE, align = "none", heights = c(1.5,1))
```

>>>>

---
title: Are kelp forests different? A comparison of kelp forests between contrasting
  study sites
output:
  pdf_document:
    toc: yes
  html_notebook:
    fig_caption: yes
    fig_height: 5
    fig_width: 4
    toc: yes
  html_document:
    df_print: paged
    toc: yes
  word_document:
    toc: yes
bibliography: mycollection.bib
---

@@

The sea urchin _P. angulosus_ is the dominant herbivore in South African kelp forests along the south-west coast [@Velimirov1977; @Field1980; @Leliaert2000] however, turbulent waters and its small size prevent it from feeding on adult kelps. Instead the urchin is restricted to feeding mostly on kelp detritus, but also on juvenile kelps [@Fricke1979; @Day2002]. The abalone Haliotis midae is also a notable herbivore in this ecosystem, but it too feeds predominantly on kelp detritus [@Tarr1996; @Mayfield2000]. This abalone is closely associated with _P. angulosus_, whereby juvenile abalone take refuge beneath urchin spines [@Day2000a; @Day2000b; @Mayfield2000].The west coast rock lobster _J. lalandii_ is known for its role in maintaining alternative stable states [@Barkai1988] and is a major predator of both _P. angulosus_ and juvenile H. midae @Mayfield2001; @BlameyBranch2012], particularly east of Cape Point where subtidal mussel beds are scarce. In the early 1990s, _J. lalandii_ expanded its distribution east of False Bay [@Cockcroft2008]. Following the ‘invasion’ of rock lobsters, herbivore numbers declined significantly, most likely as a result of direct lobster predation, which resulted in an increased abundance of macroalgae and sessile invertebrates [@Blamey2010; @Blamey2012]. This suggests that the invasion of _J. lalandii_ into these areas has resulted in the establishment of an alternative stable-state [@Blamey2012] and is an excellent example of the role that predators can play in transforming the structure and functioning of ecosystems, without directly disturbing kelp themselves.

@@

All data analyses were done using the R software (R Core Team, 2016), and the vegan package [@Oksanen2016] and ggplot2 [@Wickham2009]. The Shapiro-Wilk normality test was run before any analyses to investigate the distribution of the data. All benthic data were first 4th root transformed before any analyses were run to down-weigh species that had high biomass values and low abundance values, as this may have affected the ordination analysis. The transformed data was then used to generate a Bray-Curtis similarity matrix.

@@

```{r diversity fauna script, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap='Comparison of raw biomass species data between sites. Graph A represents flora and graph B represents fauna.'}

@@

plot_fauna <- ggplot(data = fauna_lng, aes(x = species, y= biomass, fill = site)) + 
              geom_bar(stat = "identity", show.legend = TRUE                                      ,position=position_dodge(),
              size=.3) + 
              theme(axis.text.x=element_text(angle = 90, hjust = 1, vjust = 0.3)) +
              theme(panel.background = element_rect(fill = 'white', colour =                      'white')) +
              ylab("") + 
              xlab("") +
              coord_flip()

ggarrange(plot_flora, plot_fauna, ncol = 2, nrow = 1, labels = "AUTO", legend = "bottom", common.legend = TRUE, align = "none", heights = c(1.5,1))
